% =====================================================================
%  Supplementary Material for
%  "Retrospective predictive calibration of oncology trial similarity
%   for Bayesian historical borrowing"
%
%  Standalone document. Compile with:
%     latexmk -pdf supplement.tex
%  Moved out of the main manuscript 2026-07-12 (pre-submission cleanup):
%  the Claim--Evidence Map is an internal cross-check aid and is provided
%  here as supplementary material rather than in the main appendix.
% =====================================================================
\documentclass[11pt]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage[hidelinks]{hyperref}
\setlength{\parskip}{0.4em}
\setlength{\parindent}{0pt}

\title{Supplementary Material:\\
Retrospective predictive calibration of oncology trial similarity
for Bayesian historical borrowing}
\author{}
\date{}

\begin{document}
\maketitle

\renewcommand{\thesection}{S\arabic{section}}
\renewcommand{\thetable}{S\arabic{table}}

\section{Claim--Evidence Map}

This table maps each principal claim in the main text to its supporting
evidence and the boundary of that evidence. It is a cross-check aid: every
``Status'' entry states the setting in which the claim is supported (for
example, retrospective ORR, leakage-free, simulation, or borrowing-layer only)
and does not assert clinical or regulatory validity. Numeric values match the
regenerated evidence artifacts (borrowing head-to-head $N=1{,}407$; conflict
detection from the 5{,}000-iteration operating-characteristics sweep).

\begin{longtable}{p{0.32\textwidth} p{0.39\textwidth} p{0.19\textwidth}}
\toprule
\textbf{Claim} & \textbf{Evidence} & \textbf{Status} \\
\midrule
\endhead
SECRET pool improves Stage~1 retrieval metrics over hashing. & Paired benchmark
over 1{,}470 ORR pseudo-queries with bootstrap CIs. & Supported (ORR). \\
Trained two-head calibration improves held-out NLL over rule. & $3.0562$ vs
$3.1800$ mean NLL. & Supported (retrospective ORR). \\
SAM conflict adaptation improves NLL and responds to conflict. & Two-head-SAM
$2.9328$, rule-SAM $2.9755$; simulation trigger rates. & Supported as
sensitivity evidence. \\
Conflict-adapted borrowing shows lower future-fold NLL in three rolling-origin
splits. & Leakage-free rolling-origin: rule-SAM $-0.174$ to $-0.178$;
per-fold-retrained two-head-SAM $-0.19$ to $-0.24$ nats (CIs exclude 0). &
Supported (leakage-free) for closed-form and learned models. \\
Priors are well calibrated, not merely lower loss. & PIT KS $0.146$, 95\%
coverage $0.988$ for two-head-SAM. & Supported (held-out ORR). \\
Method reduces historical influence under constructed sham-history. & Sham
controls: helps on real, not on sham; SAM triggers on sham. & Supported
(label-free; not clinical non-comparability). \\
SAM detects prior-data conflict. & Known-truth simulation: detection AUC rises
to $0.74$ (5{,}000-iter run). & Supported (simulation). \\
Learned prior outperforms a standard robust prior. & Two-head-SAM $2.933$ vs
best robust-MAP $3.135$. & Supported (retrospective ORR). \\
Conclusions insensitive to hand-set Stage~2 weights. & Tuning gains $\sim
0.013$ nats; NLL flat ($|\Delta|<0.01$). & Supported. \\
Priors not driven by individual records. & Narrow bootstrap CIs; leave-one-out
shift median $0.001$, p90 $0.015$. & Supported. \\
Borrowing-layer NLL reductions on selected other binary endpoints (exploratory).
& Leave-one-trial-out improves NLL for ORR, DCR, DLT, discontinuation (small
$n$). & Supported (borrowing-layer only; not full pipeline). \\
Extracted observations are of measured quality. & 44\% raw rows invalid;
admission rule (round-trip 8/8) removes them. & Supported. \\
Reported two-head results use a genuine two-head model. & Checkpoint
verification identified and excluded mislabeled model artifacts; the genuine
two-head checkpoint was used throughout. & Supported. \\
\bottomrule
\end{longtable}

\end{document}
